Raman sideband cooling of single sodium atom to 3D ground state

### 2017-04-19 presentations/2017-04-19_itamp/present.tex
[presentations/2017-04-19_itamp] Wave function comparison slide
[presentations/2017-04-19_itamp] Add lab member name
[presentations/2017-04-19_itamp] no legend axial plot

\documentclass{beamer}
\mode<presentation>{
  \usetheme{Boadilla}
  \usefonttheme[onlylarge]{structurebold}
  \usefonttheme[stillsansseriflarge]{serif}
  \setbeamerfont*{frametitle}{size=\normalsize,series=\bfseries}
  % \setbeamertemplate{navigation symbols}{}
  \setbeamercovered{transparent}
}
\usepackage[english]{babel}
\usepackage[latin1]{inputenc}
\usepackage{times}
\usepackage[T1]{fontenc}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{esint}
\usepackage{hyperref}
\usepackage{tikz}
\usepackage{xkeyval}
\usepackage{xargs}
\usepackage{verbatim}
\usepackage{listings}
\usepackage{multimedia}
\usepackage{bm}
\usetikzlibrary{
  arrows,
  calc,
  decorations.pathmorphing,
  decorations.pathreplacing,
  decorations.markings,
  fadings,
  positioning,
  shapes
}

@@

\title[Na ground state cooling]{Raman sideband cooling of single sodium atom to 3D ground state}
\date{April 19, 2017}
\author{Yichao Yu}
\institute{Ni Group/Harvard}

@@

@@

\begin{frame}{Rabi flopping (axial)}
  \begin{center}
    \includegraphics[width=10cm]{../../experiments/rabi_flop/imgs/fit_20170409_a1_p1_ba.png}\\
    Decoherence caused by magnetic field fluctuation.
  \end{center}
\end{frame}

>>>>

\documentclass{beamer}
\mode<presentation>{
  \usetheme{Boadilla}
  \usefonttheme[onlylarge]{structurebold}
  \usefonttheme[stillsansseriflarge]{serif}
  \setbeamerfont*{frametitle}{size=\normalsize,series=\bfseries}
  % \setbeamertemplate{navigation symbols}{}
  \setbeamercovered{transparent}
}
\usepackage[english]{babel}
\usepackage[latin1]{inputenc}
\usepackage{times}
\usepackage[T1]{fontenc}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{esint}
\usepackage{hyperref}
\usepackage{tikz}
\usepackage{xkeyval}
\usepackage{xargs}
\usepackage{verbatim}
\usepackage{listings}
\usepackage{multimedia}
\usepackage{bm}
\usepackage{siunitx}
\usetikzlibrary{
  arrows,
  calc,
  decorations.pathmorphing,
  decorations.pathreplacing,
  decorations.markings,
  fadings,
  positioning,
  shapes
}

@@

\title[Na ground state cooling]{Raman sideband cooling of single sodium atom to 3D ground state}
\date{April 19, 2017}
\author[Yichao Yu]{Yichao Yu\\
  \vspace{0.5cm}
  {\footnotesize Lee Liu, Dr. Nick Hutzler,\\
    Jessie Zhang, Dr. Jon Hood}}
\institute{Ni Group/Harvard}

@@

\begin{frame}{Wave function size}
  \begin{center}
    \begin{tikzpicture}
      \shade[ball color=blue!90] (0, 0) circle (0.45);
      \shade[ball color=orange!90] (0.4, 0.2) circle (0.3);
      \draw[<->,line width=1] (-0.45, 0.4) -- (0.35, 0.8);
      \path (-0.05, 0.6) node[rotate=26.565,above=2pt] {$4a_0$};
      \path (0.2, -2) node[below] {\textbf{Molecule}};

      \draw[line width=1] plot[samples=200,domain=-2:2,variable=\x] ({\x + 6}, {(\x)^2 * 0.8 - 1.5});
      \draw[line width=2,orange!90!black]
      plot[samples=200,domain=-2:2,variable=\x] ({\x + 6}, {exp(-(\x)^2 * 1.3) - 0.988});
      \draw[line width=0.8] (6 - 0.8, -0.988) -- (6 + 0.8, -0.988);
      \draw[<->,line width=1] (6 - 1, 0.3) -- (6 + 1, 0.3);
      \path (6, 0.3) node[above] {$1000a_0$};
      \path (6, -2) node[below] {\textbf{Atom}};
    \end{tikzpicture}
  \end{center}
\end{frame}

@@

\begin{frame}{Rabi flopping (axial)}
  \begin{center}
    \includegraphics[height=4.8cm]{../../experiments/rabi_flop/imgs/fit_20170409_a1_0_ba_nol.png}
    \includegraphics[height=4.8cm]{../../experiments/rabi_flop/imgs/fit_20170409_a1_p1_ba_nol.png}\\
    Decoherence caused by magnetic field fluctuation.
  \end{center}
\end{frame}
